\documentclass{article}
\usepackage[margin=3cm]{geometry}
\usepackage[utf8]{inputenc}
\usepackage{float}
\usepackage{graphicx} % Required for figures
\usepackage{anysize}
\usepackage{booktabs}
\usepackage{hyperref}
\usepackage{fontawesome5}
\usepackage{multirow}
\usepackage{array}
\usepackage[export]{adjustbox}
\usepackage{marvosym}
\usepackage{tabularx}
%\usepackage{ltablex}
\usepackage{tabu}
\usepackage{longtable}[=v4.13]
\usepackage{enumitem}

\title{\bfseries\Huge CV}
\begin{document}
\section*{\Huge CV}
\subsection*{Thomas Krogh Lohse}
\begin{tabularx}{\textwidth}{lX}
    \toprule%\\[-10pt]
    \href{https://maps.app.goo.gl/mtFWbUVz1f8x7saS8}{\faIcon{map-marker-alt}~Aalborg Øst 9220, Denmark}& 
    \multirow[t]{7}{=}{@!InfoText}\\\\[-4pt]
    \href{tel:+4551164199}{\faIcon{mobile-alt}~+45 51 16 41 99} \\\\[-4pt]%[8pt] 
    \href{https://github.com/t-lohse}{\faIcon{github}~\footnotesize\faIcon{at}\normalsize\texttt{t-lohse}} \\\\[-4pt]%[8pt]
    \href{https://gitlab.com/tlohse}{\faIcon{gitlab}~\footnotesize\faIcon{at}\normalsize\texttt{tlohse}} \\\\[-4pt]%[8pt]
    \href{mailto:mail@tlohse.dk}{\faIcon{envelope}~mail\normalsize\MVAt tlohse.dk} \\\\[-4pt]%[8pt]
    \href{https://linkedin.com/in/thomas-lohse}{\faIcon{linkedin}~thomas-lohse}\\\\[-4pt]
    \href{https://tlohse.dk}{\faIcon{link}~tlohse.dk}\\\\[-10pt]
    \bottomrule
\end{tabularx}%\\[8pt]
%\par\noindent\rule{\textwidth}{1pt}
\section*{@!TechSec}
\hrule width5cm

\setlength{\tabcolsep}{7pt}
\newcolumntype{Y}{>{\centering\arraybackslash}X}
\begin{longtabu} to \textwidth {YYY}
    \large%
    \textbf{@!SkillMain} & %
    \\\normalsize%
    @!SkillMainTime &%
    \\\\
    \multicolumn{3}{@{}p{\textwidth}}{\textbf{@!KnownLangTitle}
        @!KnownLangList,
    }\\[4pt]
    \multicolumn{3}{@{}p{\textwidth}}{\textbf{@!KnownToolTitle}
        @!KnownToolList,
    }
\end{longtabu}
\setlength{\tabcolsep}{6pt}

\section*{@!EduSec}
\hrule width5cm%
\begin{longtabu} to \textwidth {r|X}
@!EduStart1--@!EduEnd1 & \textbf{@!EduPlace1} \\ & @!EduDesc1 \\\\
\end{longtabu}
 
\section*{Employment}
\hrule width5cm

\begin{longtabu} to \textwidth {r|X}
2018--2019 & \textbf{Føtex Nørresundby}\\
&   Over the time of my employment at Føtex Nørresundby, I had a selection of roles:
        \begin{itemize}\setlength\itemsep{0em}
            \item[] \textbf{Service employee --- } My first contract was as a Service employee,
                with a variety of tasks, primarily the operation of the bottle recycle machine.
            \item[] \textbf{Cashier Assistant --- } About a half year after my employment,
                I was asked to be trained and reloacated to a new position, Cahsier Assistant.
            \item[] \textbf{Bake-Off Sale --- } When I turned 18 years old, and my contract
                terminated, I was offered a new position as Bake-Off Salesperson, which was my
                position up until my resignation.
        \end{itemize} \\
    2022 & \textbf{RTX A/S}\\
    &   I worked as a student assistant at RTX A/S in Nørresundby, with both hardware and software tasks,
        consisting of soldering og assembling equipment, along with developing platforms monitoring for and testing of larger devices/components. \\\\
2022--Now & \textbf{Aalborg University, DEIS}\\
    &   I work as a Student Software developer at DEIS on the \href{https://github.com/Ecdar}{Ecdar} project
    where I develop mainly in Rust in the backend engine for model checking
    (\href{https://github.com/Ecdar/Reveaal}{Reveaal}), but also contribute to the other parts of the project.\\\\
Fall 2022 & \textbf{Teaching Assistant} \\
          & I was a Teaching Assistant in the Imperative Programming course on the first semester of Software and Computer Science at AAU.
            This is the first programming course you have on the educations. I had to help students during exercise sessions, provide feedback on their hand-in assignments, and collaborate with the course lecturer regarding the exercises, platform, and hand-ins.\\\\
Fall 2023 & \textbf{Product Owner for 5th semester Software multiproject} \\
          & I was the overall product owner for the multiproject on 5th semester Software, consisting of six groups with about six members in each group. The project was 15 ECTS points.
            My responsibility included creating the tasks that should be implemented by them, answering questions regarding the code base and tasks, and generally acting as a guidance on the project, and as a PO.
\end{longtabu}
\newpage
\section*{Other Experience}
\hrule width5cm
\begin{longtabu} to \textwidth {r|X}
2021--Now & \textbf{UNF Game Development Camp}\\
&   I am a volunteer at UNFs Game Development Camp, where I have had the following roles:
    \begin{itemize}\setlength\itemsep{0em}
        \item[2021] \textbf{Programmings Assistant ---} Assisting the programming teacher, and
            helping the campers with any programming related issues they might have.
        \item[2021] \textbf{Logistics Responsible ---} In charge of handling the logistical
            requests of the other volunteers, and acquiring said logistics.
        \item[2022] \textbf{Technical Manager ---} In charge of making sure the campers'
            technical equipment is operational and set up correctly,
            along with introducing them to \texttt{git}, and managing
            the problems they might have with the technalities.
        \item[2023] \textbf{Trustee ---} One of the few contact persons regarding the weathfare of campers.
        \item[2024] \textbf{Lecture Assistant ---} Asisting in finding and acquiring lecturers to present for the campers, along with the judges for evaluating the games that are made throughout the camp.
        \item[2024] \textbf{Printing and Morning Paper Assistant ---} Assisting in acquiring permissions from game studios for artwork desiplys, and creating the morning paper for the campers.
    \end{itemize}
    \\
Fall 2021 & \textbf{Tutor}\\
&           I volunteered as a tutor for the students in 2021, studying Software at Aalborg University.\\\\
Fall 2022 & \textbf{Tutor Planner}\\
&           I volunteered as a tutor planner for the students in 2022, studying Software at Aalborg University.
            I was responsible for planning, fundraise, and execute the event, where I had to coordinate a handful of tutors to execute the event properly.\\\\
Fall 2023 & \textbf{Tutor Coordinator}\\
&           I volunteered as a tutor coordinator for the students in 2023, studying Software at Aalborg University.
            I was responsible for planning and organizing the tutor planners, making sure that they were on track with planning, fundraising, and executing their events, along with a few events I had to plan as well.
            I was also responsible for handling the finances of the orginazation, which included sending and paying invoices and budgetting.
\end{longtabu}
\iffalse
\section*{References}
\hrule width5cm \ \\
Provided upon request.
\fi

\end{document}


