\documentclass{article}
\usepackage[margin=3cm]{geometry}
\usepackage[utf8]{inputenc}
\usepackage{float}
\usepackage{graphicx} % Required for figures
\usepackage{anysize}
\usepackage{booktabs}
\usepackage{hyperref}
\usepackage{fontawesome5}
\usepackage{multirow}
\usepackage{array}
\usepackage[export]{adjustbox}
\usepackage{marvosym}
\usepackage{tabularx}
%\usepackage{ltablex}
\usepackage{tabu}
\usepackage{longtable}[=v4.13]
\usepackage{enumitem}

\title{\bfseries\Huge CV}
\begin{document}
\section*{\Huge CV}
\subsection*{Thomas Krogh Lohse}
\begin{tabularx}{\textwidth}{lX}
    \toprule%\\[-10pt]
    \href{https://goo.gl/maps/SZ6nwvdFf59X1VvR7}{\faIcon{map-marker-alt}~Sigrid Undsets Vej 156A, Aalborg Ø 9220}& 
    \multirow[t]{7}{=}{I am a 20 year ol Software, Bachelor student at Aalbog University (AAU), where I also live.
    In my spare time I enjoy learning new programming relate subjects, either by reading, or working on my own, small projects or on online learning platforms such as LeetCode.
    Examples of these could be firmware developement for my keyboard (QMK), tinkering with my Linux-environment, and optimizing upon that by creating shell-scripts mainly for automatation of tasks.
    Beyond that I also spend my spare time working.
    I have been programming since I was 16 years old.}\\\\[-4pt]
    \href{tel:+4551164199}{\faIcon{mobile-alt}~+45 51 16 41 99} \\\\[-4pt]%[8pt] 
    \href{https://github.com/LohseBoi}{\faIcon{github}~\footnotesize\faIcon{at}\normalsize\texttt{LohseBoi}} \\\\[-4pt]%[8pt]
    \href{https://gitlab.com/tlohse}{\faIcon{gitlab}~\footnotesize\faIcon{at}\normalsize\texttt{tlohse}} \\\\[-4pt]%[8pt]
    \href{mailto:mail@tlohse.dk}{\faIcon{envelope}~mail\normalsize\MVAt tlohse.dk} \\\\[-4pt]%[8pt]
    \href{https://linkedin.com/in/thomas-lohse}{\faIcon{linkedin}~thomas-lohse}\\\\[-4pt]
    \href{https://tlohse.dk}{\faIcon{link}~tlohse.dk}\\\\[-14pt]
    \bottomrule
\end{tabularx}%\\[8pt]
%\par\noindent\rule{\textwidth}{1pt}
\section*{Technical Competencies}
\hrule width5cm
\setlength{\tabcolsep}{7pt}
\begin{longtabu} to \textwidth {@{}llll}
    \centering
    \large\textbf{Software Development} & \large\textbf{git} & \large\textbf{Project Development} & \large\textbf{Linux Maintanence} \\
    \normalsize 5+ years                & 3+ years           & 4+ years                           & 2+ years \\\\
    \multicolumn{4}{@{}p{\textwidth}}{\textbf{Known Programming Languages:} Rust ($\sim$1 year),
    C\# (5+ years), C (2 years), Bash (2 years), Web (JavaScript, HTML, CSS --- 1 year), }\\[4pt]
    \multicolumn{4}{@{}p{\textwidth}}{\textbf{Known Tools:} Cargo ($\sim$1 year), \@.NET (5+ years),
    Unity (5+ years), CMake (2 years), Node.js (1 year), Electron (1 year),
    Docker ($\sim\frac{1}{2}$ year), QMK ($\sim1\frac{1}{2}$ year), GitHub (4+ years)}
\end{longtabu}
\setlength{\tabcolsep}{6pt}

\section*{Education}
\hrule width5cm
\begin{longtabu} to \textwidth {r|X}
2007--2016 & \textbf{Public School}\\
&   Attendee at the public school in 9310 Vodskov (Vodskov Skole) from grade one to grade eight.
    \\\\
2016--2017 & \textbf{Continuation School}\\
&   Attendee at Ingstrup Efterskole in grade 9.
    \\\\
2017--2020 & \textbf{High School}\\
&   High school attendee for three years at Aalborg Techcollege (AATG), and recieved the Higher
        Techincal Exam (HTX), with a specialised Study Area in \textit{Communication \& IT} A,
        \textit{Programming} B, and tecnical study in \textit{Technical Science} A. \\\\
2020--Now & \textbf{University}\\
&   Attendee at Aalborg University, studying Software Engineer, Bachelor.
    \begin{itemize}
        \item[] \textbf{1st Semester --- } Developed a workscheduling system for the production
            teams at Siemens Gamesa (Developed in C).
        \item[] \textbf{2nd Semester --- } Implemented the Signal Protocol in an IoT environment
            (Developed in JavaScript).
        \item[] \textbf{3rd Semester} Developed a program for better handling of
            Siemens Gamesas turbine blades' location and production (Developed in C\#).
        \item[] \textbf{4. Semester (Current) --- } Developed a programminglanguage as a replacement to the shell scripting language Bash (Developed in C\#).
    \end{itemize}
\end{longtabu}
 
\section*{Employment}
\hrule width5cm
\begin{longtabu} to \textwidth {r|X}
2018--2019 & \textbf{Føtex Nørresundby}\\
&   Over the time of my employment at Føtex Nørresundby, I had a selection of roles:
        \begin{itemize}\setlength\itemsep{0em}
            \item[] \textbf{Service employee --- } My first contract was as a Service employee,
                with a variety of tasks, primarily the operation of the bottle recycle machine.
            \item[] \textbf{Cashier Assistant --- } About a half year after my employment,
                I was asked to be trained and reloacated to a new position, Cahsier Assistant.
            \item[] \textbf{Bake-Off Sale --- } When I turned 18 years old, and my contract
                terminated, I was offered a new position as Bake-Off Salesperson, which was my
                position up until my resignation.
        \end{itemize} \\
    2020--Now & \textbf{RTX A/S}\\
    &   I work as a student assistant at RTX A/S in Nørresundby, with both hardware and software tasks,
        consisting of soldering og assembling equipment, along with developing platforms monitoring for and testing of larger devices/components.
\end{longtabu}

\section*{Other Experience}
\hrule width5cm
\begin{longtabu} to \textwidth {r|X}
2021--Now & \textbf{UNF Game Development Camp}\\
&   I am a volunteer at UNFs Game Development Camp, where I have had the following roles:
    \begin{itemize}\setlength\itemsep{0em}
        \item[2021] \textbf{Programmings Assistant ---} Assisting the programming teacher, and
            helping the campers with any programming related issues they might have.
        \item[2021] \textbf{Logistics Responsible ---} In charge of handling the logistical
            requests of the other volunteers, and acquiring said logistics.
        \item[2022] \textbf{Technical Manager ---} In charge of making sure the campers'
            technical equipment is operational and set up correctly,
            along with introducing them to \texttt{git}, and managing
            the problems they might have with the technalities.
    \end{itemize}
    \\
2021 & \textbf{Tutor}\\
&   I volunteered as a tutor for the students in 2021, studying Software at Aalborg University.\\
2022 & \textbf{Tutor-Planner}\\
&   I am a volunteer as a tutor-planner for the students in 2022, studying Software at Aalborg University.
\end{longtabu}

\section*{References}
\hrule width5cm \ \\
Provided upon request.

\end{document}


